---
title: "Judgement dimensionality"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is a space to work through ideas about making judgements about objects across varying levels of dimensional representation. 


At its core is the halfbaked idea that differences in judgements may in part be informed by the complexity of the space within which the judgement is being made. For example:

 - Organic food is good and non-organic food is bad, is a simple representation of a higher dimensional problem optimising issues of health, labour, environmental sustainability, etc.
 
 - Political parties are "progressive" or "conservative" is a low dimensional reduction of their status in dimensions like "economic", "authoritarian", "social" (appreciating that these themselves are abstractions of far more granular constructs)  
 
 In making judgements in these spaces, actors may vary in (1) the degree to which they reduce the dimensionality of the judgement space and also (2) in how they posit the axes of judgement. 
 
Figures below represent the projected reduction of the same 4 objects scattered in 2 dimensions onto two different axes of judgement (2).   
```{r primary-axis, echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)

df <-  tibble(obs = letters[1:4], 
              x = c(1,2,2,1), 
              y = rep(1:2, 2), 
              flat = rep(1.5, 4),
              pos = c(1, 2, 2, 1), 
              posx = c(1,2,1.5, 1.5),
              posy = posx)

p <-  ggplot(df, aes(x,y)) + 
  geom_point() + 
  geom_label(aes(label = obs), nudge_x = .05) +
  theme_bw() + 
  scale_x_continuous(breaks = 1:2, labels = c("", "")) +
  scale_y_continuous(breaks = 1:2, labels = c("", ""))

p + geom_line(aes(y = flat), colour = "red") + 
  geom_linerange(aes(ymin = y, ymax = flat), linetype = "dashed") + labs(caption = "In this axis, a and d, are equivalent, as are  b and c.")

p + geom_line(aes(y = pos), colour = "red") + 
  geom_segment(aes(y = y, yend = posy, x=x, xend = posx), linetype = "dashed") + labs(caption = "In this axis, d and c are equivalent despite having the equal largest euclidean distance of any pair of points.")
```

A stupidly late realisation is that this can be represented by the variation in weights of the underlying dimensions on the dimension of judgement. For the two scenarios presented above. 

```{r dags, warning=FALSE, message=FALSE}
library(igraph)

g1 <- graph.formula("x" -+ "judgement",
                    "y" -+ "judgement",
                      simplify = TRUE)
E(g1)$label <- c(1, 0) 
g1$layout <- layout_in_circle(g1)

plot(g1, size = 90)

g2 <- graph.formula("x" -+ "judgement",
                    "y" -+ "judgement",
                      simplify = TRUE)
E(g2)$label <- c(1, 1) 
g2$layout <- layout_in_circle(g2)
plot(g2, size = 90)


```

